---
title: "Webscraping for Task D team project"
author: "Nanyan 'Rosalie' Zhu"
date: "March 11, 2019"
output: html_document
---

```{r, echo = FALSE}
set.seed(1) # Please don't remove this code!
```

# Goal: Webscrape the Names, specialties, and phone numbers of the healthcare professionals.

# Step 1. 
1) Use the readLines() command on the urls to load the website html.
2) Create filters to screen for the lines that contain information of interest.
According to my observation, all necessary information are stored in a single line of html for every page. These lines (one per page) share a distinctive variable name "mapboxlocations".
```{r step01}
# Write a function to automate the process
doctor.info.collect <- function(page.num, url, filter){
  list.name <- list(rep(NA, page.num))
  for (page in 1:page.num){
    list.name[[page]] <- readLines(paste(url, toString(page), sep=''), warn = FALSE)
    grep(list.name[[page]], pattern = filter)
    matches.rownum <- grepl(list.name[[page]], pattern = filter)
    list.name[[page]] <- list.name[[page]][matches.rownum]
  }
  return (list.name)
}

# Define the filter that is used to locate the valuable information.
filter <- "mapboxlocations"

# Organize the Webpage page number and page url information.
page.nums <- c(19, 213, 519, 3, 29, 21, 3, 18, 25)
page.urls <- c('https://doctor.webmd.com/results?so=&city=New+York&state=NY&zip=&lat=40.7142&lon=-74.0059&ln=oncology&loc=New+York%2C+NY&pagenumber=','https://doctor.webmd.com/results?tname=Neurology&city=New%20York&state=NY&zip=&lat=40.7142&lon=-74.0059&s=501&so=&sd=29282&pagenumber=','https://doctor.webmd.com/results?so=&city=New+York&state=NY&zip=&lat=40.7142&lon=-74.0059&ln=cardiology&loc=New+York%2C+NY&pagenumber=','https://doctor.webmd.com/results?so=&city=Ann+Arbor&state=MI&zip=&lat=42.2753&lon=-83.7307&ln=oncology&loc=Ann+Arbor%2C+MI&pagenumber=','https://doctor.webmd.com/results?tname=Neurology&city=Ann+Arbor&state=MI&zip=&lat=42.2708&lon=-83.7263&s=505&so=&sd=29282&pagenumber=','https://doctor.webmd.com/results?tname=Cardiology&city=Ann+Arbor&state=MI&zip=&lat=42.2708&lon=-83.7263&s=505&so=&sd=29236&pagenumber=','https://doctor.webmd.com/results?so=&city=Nashville&state=TN&zip=&lat=36.1658&lon=-86.7844&ln=oncology&loc=Nashville%2C+TN&pagenumber=','https://doctor.webmd.com/results?so=&city=Nashville&state=TN&zip=&lat=36.1658&lon=-86.7844&ln=neurology&loc=Nashville%2C+TN&pagenumber=','https://doctor.webmd.com/results?tname=Cardiology&city=Nashville&state=TN&zip=&lat=36.1658&lon=-86.7844&s=659&so=&sd=29236&pagenumber=')

# Scrape the information we need from the webpages and store them in lists.
webMD.oncology.NY <- doctor.info.collect(page.nums[1], page.urls[1], filter)
webMD.neurology.NY <- doctor.info.collect(page.nums[2], page.urls[2], filter)
webMD.cardiology.NY <- doctor.info.collect(page.nums[3], page.urls[3], filter)
webMD.oncology.AA <- doctor.info.collect(page.nums[4], page.urls[4], filter)
webMD.neurology.AA <- doctor.info.collect(page.nums[5], page.urls[5], filter)
webMD.cardiology.AA <- doctor.info.collect(page.nums[6], page.urls[6], filter)
webMD.oncology.NV <- doctor.info.collect(page.nums[7], page.urls[7], filter)
webMD.neurology.NV <- doctor.info.collect(page.nums[8], page.urls[8], filter)
webMD.cardiology.NV <- doctor.info.collect(page.nums[9], page.urls[9], filter)
```

# Step 2.
Extract the names, phone numbers, addresses, and cities of the doctors.
```{r step02}
# Write a function to automate the process.
doctor.info.cleaning <- function(list.name, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter){
  # Generate a dataframe with 1 row. The four a's just are placeholders.
  dataframe.name <- data.frame(Name = 'a', Phone = 'a', Address = 'a', City = 'a', stringsAsFactors = FALSE)
  for (page in 1:length(list.name)){
    doctor.firstname <- regmatches(list.name[[page]], gregexpr(list.name[[page]], pattern = firstname.filter))[[1]]
    doctor.lastname <- regmatches(list.name[[page]], gregexpr(list.name[[page]], pattern = lastname.filter))[[1]]
    doctor.phone <- regmatches(list.name[[page]], gregexpr(list.name[[page]], pattern = phone.filter))[[1]]
    doctor.address <- regmatches(list.name[[page]], gregexpr(list.name[[page]], pattern = address.filter))[[1]]
    doctor.city <- regmatches(list.name[[page]], gregexpr(list.name[[page]], pattern = city.filter))[[1]]
    
    for (item in 1:length(doctor.firstname)){
      this.firstname <- substring(doctor.firstname[item], 14, nchar(doctor.firstname[item]) - 1)
      this.lastname <- substring(doctor.lastname[item], 13, nchar(doctor.lastname[item]) - 1)
      this.doctor.name <- paste(this.firstname, this.lastname)
      this.doctor.phone <- substring(doctor.phone[item], 10, nchar(doctor.phone[item]) - 1)
      this.doctor.address <- substring(doctor.address[item], 12, nchar(doctor.address[item]) - 2)
      this.doctor.city <- substring(doctor.city[item], 9, nchar(doctor.city[item]) - 1)
      
      # Populate the dataframe.
      dataframe.name <- rbind(dataframe.name, c(this.doctor.name, this.doctor.phone, this.doctor.address, this.doctor.city))
    }
  }
  # Discard the first row of the dataframe.
  dataframe.name <- dataframe.name[2:length(dataframe.name[,1]),]
  return(dataframe.name)
}

# Define the filters to extract the first and last names of the doctors.
firstname.filter <- "\"firstName\":\"([A-Z]|[a-z]|[[:space:]]|-)+\""
lastname.filter <- "\"lastName\":\"([A-Z]|[a-z]|[[:space:]]|-)+\""
# Define the filter to extract the phone numbers of the doctors.
phone.filter <- "\"phone\":\"[0-9]*\""
# Define the filters to extract the addresses and cities of the doctors.
address.filter <- "\"address\":\"([A-Z]|[a-z]|[0-9]|[[:space:]]|#|-|&|/|[.])*,\""
city.filter <- "\"city\":\"([A-Z]|[a-z]|[[:space:]])+\""

# Clean up and store the information for all cases.
doctor.oncology.NY <- unique(doctor.info.cleaning(webMD.oncology.NY, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.neurology.NY <- unique(doctor.info.cleaning(webMD.neurology.NY, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.cardiology.NY <- unique(doctor.info.cleaning(webMD.cardiology.NY, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.oncology.AA <- unique(doctor.info.cleaning(webMD.oncology.AA, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.neurology.AA <- unique(doctor.info.cleaning(webMD.neurology.AA, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.cardiology.AA <- unique(doctor.info.cleaning(webMD.cardiology.AA, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.oncology.NV <- unique(doctor.info.cleaning(webMD.oncology.NV, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.neurology.NV <- unique(doctor.info.cleaning(webMD.neurology.NV, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))
doctor.cardiology.NV <- unique(doctor.info.cleaning(webMD.cardiology.NV, firstname.filter, lastname.filter, phone.filter, address.filter, city.filter))

# Merge them to one file and add a column called "GroupID"
doctor.oncology.NY$Category <- c("Oncologist (New York)")
doctor.neurology.NY$Category <- c("Neurologist (New York)")
doctor.cardiology.NY$Category <- c("Cardiologist (New York)")
doctor.oncology.AA$Category <- c("Oncologist (Ann Arbor)")
doctor.neurology.AA$Category <- c("Neurologist (Ann Arbor)")
doctor.cardiology.AA$Category <- c("Cardiologist (Ann Arbor)")
doctor.oncology.NV$Category <- c("Oncologist (Nashville)")
doctor.neurology.NV$Category <- c("Neurologist (Nashville)")
doctor.cardiology.NV$Category <- c("Cardiologist (Nashville)")

# Add a column called "GroupID" for each dataframe. Make sure the same GroupID imply the same address in the same category.
starting_idx <- 0
doctor.oncology.NY$GroupID <- starting_idx + as.numeric(factor(doctor.oncology.NY$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.oncology.NY$Address)))
doctor.neurology.NY$GroupID <- starting_idx + as.numeric(factor(doctor.neurology.NY$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.neurology.NY$Address)))
doctor.cardiology.NY$GroupID <- starting_idx + as.numeric(factor(doctor.cardiology.NY$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.cardiology.NY$Address)))

doctor.oncology.AA$GroupID <- starting_idx + as.numeric(factor(doctor.oncology.AA$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.oncology.AA$Address)))
doctor.neurology.AA$GroupID <- starting_idx + as.numeric(factor(doctor.neurology.AA$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.neurology.AA$Address)))
doctor.cardiology.AA$GroupID <- starting_idx + as.numeric(factor(doctor.cardiology.AA$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.cardiology.AA$Address)))

doctor.oncology.NV$GroupID <- starting_idx + as.numeric(factor(doctor.oncology.NV$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.oncology.NV$Address)))
doctor.neurology.NV$GroupID <- starting_idx + as.numeric(factor(doctor.neurology.NV$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.neurology.NV$Address)))
doctor.cardiology.NV$GroupID <- starting_idx + as.numeric(factor(doctor.cardiology.NV$Address))
starting_idx <- starting_idx + length(levels(factor(doctor.cardiology.NV$Address)))

doctor.summary <- data.frame(Name = character(), Phone = character(), Address = character(), City = character(), Category = character(), GroupID = integer())
doctor.summary <- rbind(doctor.summary, doctor.oncology.NY)
doctor.summary <- rbind(doctor.summary, doctor.neurology.NY)
doctor.summary <- rbind(doctor.summary, doctor.cardiology.NY)
doctor.summary <- rbind(doctor.summary, doctor.oncology.AA)
doctor.summary <- rbind(doctor.summary, doctor.neurology.AA)
doctor.summary <- rbind(doctor.summary, doctor.cardiology.AA)
doctor.summary <- rbind(doctor.summary, doctor.oncology.NV)
doctor.summary <- rbind(doctor.summary, doctor.neurology.NV)
doctor.summary <- rbind(doctor.summary, doctor.cardiology.NV)
```

# Step 3.
Save the resulting 10 dataframes as csv files.
```{r step03}
write.csv(doctor.summary, file = "Doctor_Summary.csv")
write.csv(doctor.oncology.NY, file = "Oncology_NewYork.csv")
write.csv(doctor.neurology.NY, file = "Neurology_NewYork.csv")
write.csv(doctor.cardiology.NY, file = "Cardiology_NewYork.csv")
write.csv(doctor.oncology.AA, file = "Oncology_AnnArbor.csv")
write.csv(doctor.neurology.AA, file = "Neurology_AnnArbor.csv")
write.csv(doctor.cardiology.AA, file = "Cardiology_AnnArbor.csv")
write.csv(doctor.oncology.NV, file = "Oncology_Nashville.csv")
write.csv(doctor.neurology.NV, file = "Neurology_Nashville.csv")
write.csv(doctor.cardiology.NV, file = "Cardiology_Nashville.csv")
```

Also save the 9 lists as RData
```{r save}
save(webMD.oncology.NY, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.oncology.NY.Rdata")
save(webMD.neurology.NY, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.neurology.NY.Rdata")
save(webMD.cardiology.NY, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.cardiology.NY.Rdata")
save(webMD.oncology.AA, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.oncology.AA.Rdata")
save(webMD.neurology.AA, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.neurology.AA.Rdata")
save(webMD.cardiology.AA, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.cardiology.AA.Rdata")
save(webMD.oncology.NV, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.oncology.NV.Rdata")
save(webMD.neurology.NV, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.neurology.NV.Rdata")
save(webMD.cardiology.NV, file = "C:/Users/ChenRaphaelLiu/Desktop/Columbia Courses/Rosalie/More Data/webMD.cardiology.NV.Rdata")
```